SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-23 authors.tex
Fixing more typos

\author{
Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, and Rui~Xue\altaffilmark{1}
}
\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
\altaffiltext{2}{Insititute for Astronomy, University of Hawaii, Honolulu, HI 96822}
\altaffiltext{3}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
\altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
\altaffiltext{5}{Department of Physics, Hebei Normal University, 20 South Erhuan Road, Shijiazhuang, 050024, China}
\altaffiltext{6}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical Observatory, Chinese Academy of Sciences, 80 Nandan Road, Shanghai 200030, China}
\altaffiltext{7}{University of the Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}

>>>>

\author{
Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
}
\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
\altaffiltext{2}{Insititute for Astronomy, University of Hawaii, Honolulu, HI 96822}
\altaffiltext{3}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
\altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
\altaffiltext{5}{Department of Physics, Hebei Normal University, 20 South Erhuan Road, Shijiazhuang, 050024, China}
\altaffiltext{6}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical Observatory, Chinese Academy of Sciences, 80 Nandan Road, Shanghai 200030, China}
\altaffiltext{7}{University of the Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}

### 2020-10-23 maintex.tex
Fixing more typos

%%%Galaxy Evolution%%%
In the $\Lambda$CDM model, galaxy evolution is a hierarchical process. In this model, massive galaxies are the product of several past merger events of smaller galaxies. In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 \citep[e.g.,][]{Rodriguez-Gomez:2016,Pillepich:2018}. As the galaxies undergo the merging process, the gas within the galaxies are subject to gravitational torques which perturb the morphology of the galaxies.

%%%Simulations%%%
The internal dynamics of these interacting galaxies were first modeled in the seminal work, \citet{Toomre:1972}. Since then, hydrodynamical simulations have expanded upon the N-body simulations of \citet{Toomre:1972} by modeling gas-dynamics within the galaxies. These simulations show how barred structures develop within the disks of the interacting galaxies due to the tidal torques between them \citep{Barnes:1991}. As the bars form, the gases within the galaxy's disk lose angular momentum and get funneled into the centers of the galaxies.

When the gas-inflows impact upon the gases in the nucleus of galaxy a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}. These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}. The gas-inflows may also be able to reach the very center of the galaxy and trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.

%%%Observations%%%
Interaction induced star formation was first seen observationally in the bluer colors of peculiar galaxies in \citet{Larson:1978}. This observation has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}. From these previous works it has been shown that the strength of the star formation enhancement in the centers of paired galaxies is dependent on the stellar mass of the pairs \citep{Li:2008}, the projected separation between the pairs \citep{Ellison:2008, Li:2008, Scudder:2012}, and the mass ratio between the pairs \citep{Ellison:2008}.

%%%Integral Field Spectroscopy%%%
The previous mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers. With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail. These surveys allow us to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture. These IFS surveys will also allow us to see the extent of the centrally induced star formation and to see how the star formation in the disks of the galaxies are affected.

Indeed, \citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted from. In this study, they found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.

\citet{Pan:2019} used the SDSS-IV MaNGA survey to study radial profiles of a sample of 205 paired galaxies. The enhancement to the sSFR was shown to be the strongest in the centers of the paired galaxies. This central enhancement linearly fell with increasing galactocentric radii; however, a moderate enhancement to the sSFR remain in the outskirts of the galaxies. \citet{Pan:2019} further studied the paired galaxies as a function of merger stage; from well separated pairs to post-merger galaxies. Across the different merger stages, the sSFR enhancement was greatest in close pairs with tidal features and in post-merger galaxies. This was in agreement with previous hydrodynamical simulations which showed that a burst of star formation is triggered after the first pericenter and as the two galaxies begin to coalesce \citep{Scudder:2012}.

@@

Where previous studies on the radial profile of the sSFR offsets in paired galaxies have focused on studying the profiles as a function of interaction stage, we will focus on the radial profile as a function of the stellar mass, projected separation, and mass ratio. As mentioned previously, these parameters have been covered by studies restricted to the nuclear region of the paired galaxies. With the MaNGA survey, we will be able to expand upon these previous studies in greater spatial detail. We will be able to see how these three parameters affect both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies. We will also be able to study if any of three parameters influence the gradient of the sSFR enhancement profiles or if the gradient is preserved between different configurations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

MaNGA is an IFS survey at the Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}. MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citep{Law:2015}. MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a PSF of 2.5\arcsec\ FWHM \citep{Bundy:2015}.

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18)
\end{equation}

Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}. Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.

@@

The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects. The ``good" galaxy spectra are the objects whose spectra are well modeled by {\sc spfit} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy. This means that the companion galaxy can be within approximately $\pm$3000 km s$^{-1}$ of the MaNGA target. We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.

Among 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU. We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions. Given redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc. Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples. We also require that the galaxies are classified as star forming as described in Section \ref{sec:data}. These requirements reduce our sample down to 87 star forming MaNGA targets with inside-IFU companions. While the companions to the inside-IFU MaNGA targets contained are within the MaNGA IFUs, we only use the MaNGA targets when building radial profiles. We leave out the identified companions from the analysis because the MaNGA targets are covered by the NSA catalog with geometries and total stellar masses while the companions are not covered by the NSA catalog.

@@

From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets. After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. This give use a total of 175 MaNGA targets in our pair sample.

@@

In the first method, we only control for the stellar mass between the pairs and controls. We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5. The pairs are then compared to their respective controls within each stellar mass bin. While the redshift in not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.

@@

We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.

@@

Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the stellar mass in the same spaxel, giving us the specific star formation rate (sSFR):
\begin{equation}
{\rm sSFR} = \frac{\rm SFR}{M}
\end{equation}
The local stellar masses used here is derived from {\sc SPFIT}'s best-fit stellar continuum. Utilizing sSFR, instead of SFR, allows us to compare regions of high mass surface density to regions of low mass surface density.

@@

We fit the geometry with apertures from both catalogs when available. When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures. When making the comparison with the second tailored control method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures. Further, when defining the a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.

@@

\begin{equation}
{\rm cos^2}(i) = \frac{(b/a)^2 - q^2}{1 - q^2}
\end{equation}

Where $b/a$ is the major-to-minor axis ratio and $q$ is the intrinsic oblateness. We use the empirically determined oblateness of $q = 0.13$, from \citet{Giovanelli:1994}.

The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies. We use the 50\% half light radius (i.e. the effective radius, \reff) to scale the sizes of the galaxies. Doing this will allow us to compare galaxies of different sizes against each other.

Once the geometry of the galaxies are set, we can build azimuthally averaged radial profiles. The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. The parts of the profiles with dashed lines represent regions where less than 50\% of the galaxies in the bin are covered at that radii. }
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

With the individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies. The first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins. In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which are matched in stellar mass and redshift.

@@

{\bf COMMENT: I am not sure the trimmed regions could be so limited. If this is indeed correct, then we don't need to spend a paragraph on something so negligible and not to highlight the trimed regions in the plots.} 
The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy. Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin. Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin. To account for this, we ``trim" the stacked profiles where a radius bin contains data for less than 50\% of the total set of galaxies. We represent the trimmed regions in our figures with dashed lines. In Figure \ref{fig:ssfr_prof}, galaxies below \logm\ $\le$ 10.0 have their innermost radii bin trimmed due to insufficient coverage.

We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space). This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.35$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff. In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex). As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.

@@

The sSFR as a function of separation was studied with the cosmological hydrodynamical simulations of IllustrisTNG \citep{Patton:2020}. In Figure \ref{fig:nuc_sep} we show the $\Delta$log(sSFR) enhancements across 2D separation (projected separation) from the TNG300-1 simulation. \citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2d separation of $\sim$250 kpc. This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in Figure \ref{fig:nuc_sep} was extracted from a 0.5 \reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius. This means that our extraction radius is effectively twice a small and is more restricted to the central burst of star formation.

>>>>

%%%Galaxy Evolution%%%
In the $\Lambda$CDM model, galaxy evolution is a hierarchical process. In this model, massive galaxies are the product of several past merger events of smaller galaxies. In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 \citep[e.g.,][]{Rodriguez-Gomez:2016,Pillepich:2018}. As the galaxies undergo the merging process, the gas within the galaxies are subjected to gravitational torques which perturb the morphology of the galaxies.

%%%Simulations%%%
The internal dynamics of these interacting galaxies were first modeled in the seminal work, \citet{Toomre:1972}. Since then, hydrodynamical simulations have expanded upon the N-body simulations of \citet{Toomre:1972} by modeling gas-dynamics within the galaxies. These simulations show the process by which barred structures develop within the disks of the interacting galaxies due to the tidal torques between them \citep{Barnes:1991}. As the bars form, the gases within the galaxy's disk lose angular momentum and get funneled into the centers of the galaxies.

When the gas-inflows impact upon the gases in the nucleus of the galaxy, a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}. These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}. The gas-inflows may also be able to reach into the very center of the galaxy and trigger an episode of supermassive black hole (SMBH) accretion \citep{Capelo:2017}.

%%%Observations%%%
Interaction induced star formation was first seen observationally in the bluer colors of peculiar galaxies in \citet{Larson:1978}. Similar observations have has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}. From these previous works it has been shown that the strength of the star formation enhancement in the centers of paired galaxies is dependent on the stellar mass of the pairs \citep{Li:2008}, the projected separation between the pairs \citep{Ellison:2008, Li:2008, Scudder:2012}, and the mass ratio between the pairs \citep{Ellison:2008}.

%%%Integral Field Spectroscopy%%%
The previously mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers. With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail. These surveys allow us to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture. These IFS surveys will also allow us to see the extent of the centrally induced star formation and to see how the star formation in the disks of the galaxies are affected.

Indeed, \citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted. In this study, they found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.

\citet{Pan:2019} used the SDSS-IV MaNGA survey to study radial profiles of a sample of 205 paired galaxies. The enhancement to the sSFR was shown to be the strongest in the centers of the paired galaxies. This central enhancement linearly fell with increasing galactocentric radii; however, a moderate enhancement to the sSFR remains in the outskirts of the galaxies. \citet{Pan:2019} further studied the paired galaxies as a function of merger stage, from well separated pairs to post-merger galaxies. Across the different merger stages, the sSFR enhancement was greatest in close pairs with tidal features and in post-merger galaxies. This was in agreement with previous hydrodynamical simulations which showed that a burst of star formation is triggered after the first pericenter and as the two galaxies begin to coalesce \citep{Scudder:2012}.

@@

Where previous studies on the radial profile of the sSFR offsets in paired galaxies have focused on studying the profiles as a function of interaction stage, we will focus on the radial profile as a function of the stellar mass, projected separation, and mass ratio. As mentioned previously, these parameters have been covered by studies restricted to the nuclear region of the paired galaxies. With the MaNGA survey, we will be able to expand upon these previous studies in greater spatial detail. We will be able to analyze how these three parameters affect both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies. We will also be able to study whether any of the three parameters influence the gradient of the sSFR enhancement profiles or if the gradient is preserved between different configurations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

MaNGA is an IFS survey at the Apache Point Observatory (APO) which uses the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}. MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers: 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citep{Law:2015}. MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a PSF of 2.5\arcsec\ FWHM \citep{Bundy:2015}.

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18),
\end{equation}
Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}. Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.

@@

The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories: ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects. The ``good" galaxy spectra are the objects whose spectra are well modeled by {\sc spfit} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy. This means that the companion galaxy can be within approximately $\pm$3000 km s$^{-1}$ of the MaNGA target. We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.

Among the 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU. We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions. Given the redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc. Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples. We also require that the galaxies are classified as star forming as described in Section \ref{sec:data}. These requirements reduce our sample down to 87 star forming MaNGA targets with inside-IFU companions. While the companions to the inside-IFU MaNGA targets contained are within the MaNGA IFUs, we only use the MaNGA targets when building radial profiles. We leave out the identified companions from the analysis because the MaNGA targets are covered by the NSA catalog with geometries and total stellar masses while the companions are not covered by the NSA catalog.

@@

From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets. After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. This gives us a total of 175 MaNGA targets in our pair sample.

@@

In the first method, we only control for the stellar mass between the pairs and controls. We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5. The pairs are then compared to their respective controls within each stellar mass bin. While the redshift is not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.

@@

We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.

@@

Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the stellar mass in the same spaxel, giving us the specific star formation rate (sSFR):
\begin{equation}
{\rm sSFR} = \frac{\rm SFR}{M}.
\end{equation}
The local stellar masses used here is derived from {\sc spfit}'s best-fit stellar continuum. Utilizing sSFR, instead of SFR, allows us to compare regions of high mass surface density to regions of low mass surface density.

@@

We fit the geometry with apertures from both catalogs when available. When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures. When making the comparison with the second tailored control method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures. Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.

@@

\begin{equation}
{\rm cos^2}(i) = \frac{(b/a)^2 - q^2}{1 - q^2},
\end{equation}
Where $b/a$ is the major-to-minor axis ratio and $q$ is the intrinsic oblateness. We use the empirically determined oblateness of $q = 0.13$, from \citet{Giovanelli:1994}.

The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies. We use the 50\% half light radius ({\it i.e}, the effective radius, \reff) to scale the sizes of the galaxies. Doing this will allow us to compare galaxies of different sizes against each other.

Once the geometries of the galaxies are set, we can build azimuthally averaged radial profiles. The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. }
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

With the individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies. In the first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins. In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which are matched in stellar mass and redshift.

@@

%{\bf COMMENT: I am not sure the trimmed regions could be so limited. If this is indeed correct, then we don't need to spend a paragraph on something so negligible and not to highlight the trimed regions in the plots.} 
%The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy. Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin. Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin. To account for this, we ``trim" the stacked profiles where a radius bin contains data for less than 50\% of the total set of galaxies. We represent the trimmed regions in our figures with dashed lines. In Figure \ref{fig:ssfr_prof}, galaxies below \logm\ $\le$ 10.0 have their innermost radii bin trimmed due to insufficient coverage.

We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space). This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.35$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff. In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex). As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.

@@

The sSFR as a function of separation was studied with the cosmological hydrodynamical simulations of IllustrisTNG \citep{Patton:2020}. In Figure \ref{fig:nuc_sep} we show the $\Delta$log(sSFR) enhancements across 2D separation (projected separation) from the TNG300-1 simulation. \citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2D separation of $\sim$250 kpc. This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in Figure \ref{fig:nuc_sep} was extracted from a 0.5 \reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius. This means that our extraction radius is effectively twice a small and is more restricted to the central burst of star formation.
